Cleaning Foregrounds and Boosting Signals with Multi-line Intensity Mapping

### 2019-07-16 paper/ms.tex
Update title
Add start of intro

\newcommand{\CI}{\ensuremath{\text{C~\textsc{i}}}}
\newcommand{\CII}{\ensuremath{\text{C~\textsc{ii}}}}
\newcommand{\OIII}{\ensuremath{\text{O~\textsc{iii}}}}
\newcommand{\CO}{\ensuremath{\text{CO}}}

@@

\title{Multi-line Intensity Mapping}

@@

\section{Introduction}\label{sec:intro}

@@

We note that in this model the redshift evolution of each line is identical up
to the luminosity-SFR constant of proportionality. In reality, we do not
expect this to be the case. For example, the different CO lines should have
varying intrinsic strengths since the typical phase of the ISM in each
emitting galaxies should change as a function of redshift. This highlights one
of the limitations of the line intensity model adopted here. Fully
understanding the underlying galactic population will require more nuanced
models, though the best path forward is not clear.

>>>>

\newcommand{\CI}{\ensuremath{\text{C~\textsc{i}}}}
\newcommand{\CII}{\ensuremath{\text{C~\textsc{ii}}}}
\newcommand{\OIII}{\ensuremath{\text{O~\textsc{iii}}}}
\newcommand{\CO}{\ensuremath{\text{CO}}}
\newcommand{\HI}{\ensuremath{\text{H~\textsc{i}}}}

@@

\title{Cleaning Foregrounds and Boosting Signals with Multi-line Intensity Mapping}

@@

\section{Introduction}\label{sec:intro}
Precision studies of the large-scale structure (LSS) of the universe provide
important cosmological constraints. Traditional galaxy surveys are limited in
their possible redshift extent to currently $z\lesssim1$ due to the expense
required in taking spectra of large numbers of high-redshift galaxies.
Line-intensity mapping has emerged as a promising alternative, instead
measuring the collective emission in a convenient line in fairly coarse
pixels. By sacrificing resolution, intensity mapping allows one to measure
large scales at high redshift.

Intensity mapping of the $\HI$~21~cm line is the most well studied. During
reionization, it is sourced by the intergalactic medium . Post-reionization,
it is sourced by neutral hydrogen primarily in the interstellar medium . A
detection of the 21~cm power spectrum and the baryon acoustic oscillation
feature have been made at $z\sim0.8$ \citep{2010Natur.466..463C}.

@@

We note that in this model the redshift evolution of each line is identical up
to the luminosity-SFR constant of proportionality. In reality, we do not
expect this to be the case. For example, the different CO lines should have
varying intrinsic strengths since the typical phase of the ISM in each
emitting galaxies should change as a function of redshift. This highlights one
of the limitations of the line intensity model adopted here. Fully
understanding the underlying galactic population will require more nuanced
models, on which development is underway ({\bf cite}).
